comgen-outline

### 2017-11-18 paper/case1-generics.Rmd
fix sectioning

In this experiment, we elicit human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].
The goal of this study is to observe a range of endorsements for generic statements about animal categories.

#### Method
```{r eval = F}
d1 <- read.csv(paste(project.path, "data/generics/endorsement/",
                    "truth-judgments-n100.csv", sep = ""))
d2 <- read.csv(paste(project.path, "data/generics/endorsement/",
                    "naturalGenerics-trials-formatted.csv", sep = ""))

@@

##### Participants

@@

##### Procedure and materials

@@

#### Results

@@

### Uncertain threshold RSA model

>>>>

In this experiment, we elicit human endorsements for generalizations about categories (*generics*) taken from the linguistic and psychological literature on generics [@Prasada2013].
The goal of this study is to observe a range of endorsements for generic statements about animal categories.

### Method
```{r eval = F}
d1 <- read.csv(paste(project.path, "data/generics/endorsement/",
                    "truth-judgments-n100.csv", sep = ""))
d2 <- read.csv(paste(project.path, "data/generics/endorsement/",
                    "naturalGenerics-trials-formatted.csv", sep = ""))

@@

@@

@@

@@

#### Uncertain threshold model
